Assessing Digital Elevation Models with different image overlap using photogrammetry

### 2021-05-02 Paper.tex
Updates from Overleaf

% KAO: Use times symbol
\abstract{
Photogrammetry is easy to use these days and can be used to create a digital elevation models (DEM) of an area. 
Image overlap plays an important role in the process of photogrammetry.
A high overlap takes more time to gather in the field and takes longer to process.
Less overlap usually results in a less accurate calculations. 
In this paper the overlap of an area is artificially reduced.
The image count does have a positive influence on the sparse cloud, but no influence on the points in the dense cloud.
The DEM's are compared to see how reducing the image overlap influences the DEM result. 
When the absolute values of the DEM are compared large differences are visible.
However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
Finally, violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
The more images are used, the more the difference of the DEM's is centered around 0.
The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
}

@@

The violin plots indicate that the dataset with the highest image count is most similar to the full dataset; the difference of is more centered around zero, while the two lower image count datasets are more widespread.
The largest errors differences (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
This is confirmed by looking at the difference between the scaled DEM's in \ref{fig:ScaledDifference}.
The modelling software seems to have difficulties in modelling the complex structures of the vegetation with a lower image count, resulting in a larger difference when the image count is lower.
This could result in more error around vegetation canopies where the algorithm has difficulties in accurately measuring the height. 
\citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results. 
However, in this research this is only visibly assessed as the vegetation locations have not been extracted from the full image dataset.
An other option may changing the filtering setting provided by the Metashape dense cloud generation.
In this research no depth filtering was used, by applying a more aggressive filtering technique the complex structures of the vegetation will be lost in the DEM generation \citep{AgisoftMetashape}.
Further research is needed to see where this differences exactly occur and if a different depth filtering may result in different results.

>>>>

% KAO: Use times symbol
\abstract{
Photogrammetry is easy to use these days and can be used to create a digital elevation models (DEM) of an area. 
Image overlap plays an important role in the process of photogrammetry.
A high overlap takes more time to gather in the field and takes longer to process.
Less overlap usually results in a less accurate calculations. 
In this paper the overlap of an area is artificially reduced.
The image count does have a positive influence on the sparse cloud, but no influence on the points in the dense cloud.
The DEM's are compared to see how reducing the image overlap influences the DEM result. 
When the absolute values of the DEM are compared large differences are visible.
However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
Finally, violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
The more images are used, the more the difference of the DEM's is centered around 0.
The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
The differences between the DEM's seem to occur around vegetation.
}

@@

The violin plots indicate that the dataset with the highest image count is most similar to the full dataset; the difference of is more centered around zero, while the two lower image count datasets are more widespread.
The largest errors differences (around -5/5) between the scaled DEM seem to be the same for all the image datasets.
This is confirmed by looking at the difference between the scaled DEM's in \ref{fig:ScaledDifference}.
The modelling software seems to have difficulties in modelling the complex structures of the vegetation with a lower image count, resulting in a larger difference when the image count is lower.
This could result in more error around vegetation canopies where the algorithm has difficulties in accurately measuring the height. 
\citet{AccessingImageOverlap} also concluded that for complex structures a higher image overlap provides better results.
However, in this research this is only visibly assessed as no ground truth vegetation locations have not been extracted from the full image dataset.

An other option may changing the filtering setting provided by the Metashape dense cloud generation.
In this research no depth filtering was used, by applying a more aggressive filtering technique the complex structures of the vegetation will be lost in the DEM generation \citep{AgisoftMetashape}.
Further research is needed to see where this differences exactly occur and if a different depth filtering may result in different results.
